%&LaTeX

\chapter{Assembly}
The linear system assembly phase is where matrix and rhs-vector contributions
are added, using sum-into APIs.

Nalu computes matrix and rhs-vector contributions in classes which are derived
from the \code{Kernel} base-class. These kernels include computations such as
continuity-advection, momentum-advection-diffusion, and many others. These kernels
are called within an algorithm which manages mesh traversal, handles the gathering
of field-data and master-element computations, etc. The following pseudo-code shows
the execution or flow of these algorithms.

\begin{verbatim}
select buckets for part(s) that algorithm is applied to

for each selected bucket {
   ScratchViews scratch(gathered fields);

   for each elem in bucket {
        fill_scratch_views(scratch, ...);

        for each active kernel {
           kernel->execute(lhs, rhs, scratch);
        }
        sum_into_linear_system(lhs, rhs);
    }
}
\end{verbatim}

Note that in the above pseudo-code, \code{fill\_scratch\_views} includes both
gathering needed field-data as well as making master-element calls such
as grad-op, etc.

Note also that significant detail has been omitted, such as the handling of
SIMD sub-looping, interleaving the SIMD data, etc.  To see the actual algorithm code,
see the Nalu classes \code{AssembleElemSolverAlgorithm},
and \code{AssembleFaceElemSolverAlgorithm}.

The \code{sum\_into\_linear\_system} step is where the computed coefficients are
contributed to the linear-system. This is done by obtaining the local matrix from the
\code{Tpetra::CrsMatrix} object using the method \code{getLocalMatrix()} and then
summing directly into that. Similarly, rhs coefficients are summed into the \code{Kokkos::View}
provided by the \code{getLocalView} method of \code{Tpetra::Vector}.

Recall that we are operating on two matrix objects, \code{ownedMatrix\_} and
\code{sharedNotOwnedMatrix\_}. During this sum-into process, coefficients are added
to the appropriate matrix (and rhs-vector) depending on whether they are associated
with an owned or shared mesh node. Once all local assembly is complete, the shared matrix
is then communicated and added to the local matrix using \code{Tpetra} operations, called
from within the Nalu method \code{TpetraLinearSystem::loadComplete()}:

\begin{verbatim}
sharedNotOwnedMatrix_->fillComplete();

ownedMatrix_->doExport(*sharedNotOwnedMatrix_, *exporter, Tpetra::ADD);

ownedMatrix_->fillComplete();

ownedRhs_->doExport(*sharedNotOwnedRhs_, *exporter_, Tpetra::ADD);
\end{verbatim}

\section{Boundary condition enforcement}

Dirichlet boundary conditions are enforced by modifying the appropriate rows
of the assemled linear system before calling the linear-solver.

Insert pseudo-code for dirichlet BC enforcement here.

