\section{Performance Results}
\label{s:results}
In this section, performance results are provided for the Nalu code base
using a variety of platforms including Haswell, KNL, and classic Sandy Bridge
architectures.

\subsection{Consolidated Design using Kokkos-based Computational Kernels}

The performance improvements for the matrix assembly timings with the new Kokkos
and SIMD enabled computations were benchmarked on the NERSC
Cori\footnote{\url{http://www.nersc.gov/users/computational-systems/cori/configuration/}}
machine. The code was benchmarked on both the Haswell and KNL partitions on the
machine for the open-jet test case with the following meshes: 1) coarse
low-order ($P=1$) mesh (17.5M \code{HEXAHEDRAL-8} elements); 2) fine low-order
($P=1$) mesh (140M \code{HEXAHEDRAL-8} elements); and 3) a high-order ($P=2$)
mesh obtained using element promotion of the coarse low-order mesh once ($17.5$M
\code{HEXAHEDRAL-27} elements). The non-consolidated kernel design from the
original Nalu source code was chosen as the baseline for performance
comparisons. The performance was then benchmarked successively for various
algorithmic design changes introduced in the code:

\begin{description}
\item[Hybrid] The default production run setup used in Nalu before ExaWind
  project. This configuration is termed \emph{hybrid} because it mixes element
  contributions and nodal source contributions while assembling the terms in the
  Navier-Stokes equation. The hybrid method eliminates the necessity to perform
  sub-control volume calculations that is necessary for the lumped-mass element
  source terms that will be used in a pure element-based algorithm
  implementation. While the matrix assembly timings of the \emph{hybrid}
  implementation is not a correct baseline for evaluating the gains from
  Kokkos-based threading and SIMD vectorization, it does however, provide an
  estimate of the actual gains that a casual Nalu user might observe when moving
  from the current release to the latest version used in this project.
  Furthermore, a hybrid configuration does not provide design order of accuracy
  for high-order meshes. Therefore, this configuration is only run for the
  low-order meshes. A transition strategy to support nodal-based assembly
  is captured in section~\ref{s:pathForward}.
\item[Baseline B] Lumped mass element based source terms for consistent assembly
  timing comparison with the consolidated algorithm design explored in this
  study.
\item[Configuration C1] Consolidated Kernel design using \code{ScratchViews} and element data
  registration (Sec.~\ref{sec:scratchviews}). This configuration uses all the
  terms used in the Baseline.
\item[Configuration C2] Consolidated Kernels with SIMD datatype (i.e.,
  \code{DoubleType} is set to \code{stk::simd::Double}) -- see
  Sec.~\ref{sec:simd_vectorization}.
\item[Configuration C3] Consolidated Kernels with SIMD on multiple OpenMP threads.
\item[Configuration C4] Improvements to \emph{SIMD interleave} code and matrix \code{sumInto}
  logic based on performance analysis using VTune from last step.
\end{description}


The matrix assembly times were compared for the four equation systems: momentum,
continuity, turbulence kinetic energy (TKE), and mixture fraction.
Tables~\ref{tab:haswell_assembly_timings} and \ref{tab:knl_assembly_timings}
show the matrix assembly timings for the four equation systems on Cori's
Haswell and KNL partitions respectively. Table~\ref{tab:run_conf} shows the MPI
and OpenMP settings that were used for the various runs. To account for the
differences in the clock speeds and machine architectures between Haswell and
KNL, the simulations were performed on twice the number of MPI ranks on KNL as
compared to Haswell. On most runs, the comparison is done on the basis of number
of nodes instead of the same MPI ranks.

\begin{table}[!htb]
  \centering
  \caption{Table showing the details of parallel execution (MPI ranks and OpenMP
    threads) for the various code configuration results shown in this section.}
  \label{tab:run_conf}
  \begin{tabular}{l||r|r|r|r|r|r|r|r}
    \hline\hline
     & \multicolumn{4}{c|}{\textbf{Haswell}} & \multicolumn{4}{c}{\textbf{KNL}} \\ [0.5em]
    Code & Num. & MPI & Ranks per & OMP & Nodes & MPI & Ranks per & OMP \\
    Configuration & Nodes & ranks & node & Threads & Nodes & ranks & node & Threads\\ [1em]
    \multicolumn{8}{l}{\textbf{Coarse $P=1$ mesh (17.5M HEX-8 elements)}} \\
    \hline
    Hybrid & 5 & 160 & 32 & 1 & 5 & 320 & 64 & 1\\
    Baseline & 5 & 160 & 32 & 1 & 5 & 320 & 64 & 1\\
    C1 & 5 & 160 & 32 & 1 & 5 & 320 & 64 & 1\\
    C2 & 5 & 160 & 32 & 1 & 5 & 320 & 64 & 1\\
    C3 & 10 & 160 & 16 & 2 & 5 & 320 & 64 & 2\\
    C4 & 10 & 160 & 16 & 2 & 5 & 320 & 64 & 2\\ [1em]
    \multicolumn{8}{l}{\textbf{Fine $P=1$ mesh (140M HEX-8 elements)}} \\
    \hline
    Hybrid & 40 & 1280 & 32 & 1 & 40 & 2560 & 64 & 1\\
    Baseline & 40 & 1280 & 32 & 1 & 40 & 2560 & 64 & 1\\
    C1 & 40 & 1280 & 32 & 1 & 40 & 2560 & 64 & 1\\
    C2 & 40 & 1280 & 32 & 1 & 40 & 2560 & 64 & 1\\
    C3 & 80 & 1280 & 16 & 2 & 40 & 2560 & 64 & 2\\
    C4 & 80 & 1280 & 16 & 2 & 40 & 2560 & 64 & 2\\ [1em]
    \multicolumn{8}{l}{\textbf{Coarse $P=2$ mesh (17.5M HEX-27 elements)}} \\
    \hline
    Baseline & 40 & 1280 & 32 & 1 & 40 & 2560 & 64 & 1\\
    C1 & 40 & 1280 & 32 & 1 & 40 & 2560 & 64 & 1\\
    C2 & 40 & 1280 & 32 & 1 & 40 & 2560 & 64 & 1\\
    C3 & 80 & 1280 & 16 & 2 & 80 & 2560 & 32 & 2\\
    C4 & 80 & 1280 & 16 & 2 & 80 & 2560 & 32 & 2\\
    \hline\hline
  \end{tabular}
\end{table}

\begin{landscape}
  \begin{table}[tb]
    \centering
    \caption{Matrix assembly timing comparisons on Haswell partition of NERSC Cori
      system. Code configurations: H -- Hybrid element/node algorithm; B --
      Baseline non-consolidated algorithm; C1 -- consolidated kernel algorithms; C2 --
      C1 with SIMD datatypes; C3 -- C2 with OpenMP threading; C4 -- C3 with
      \code{sumInto(...)} and SIMD interleave optimizations.}
    \label{tab:haswell_assembly_timings}
    \begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r}
      \hline\hline
      & \multicolumn{6}{c|}{Matrix assembly time (s)} & \multicolumn{7}{c}{Speedup ratio} \\[0.5em]
      Equation & Hybrid & Baseline & Conf. C1 & Conf. C2 & Conf. C3 & Conf. C4 & B:C1 & C1:C2 & B:C2 & B:C3 & B:C4  & H:B & H:C4\\ [1em]
      \multicolumn{10}{l}{\textbf{Coarse $P=1$ mesh (17.5M HEX-8 elements)}} \\
      \hline
      Momentum & 233.9 & 264.5 & 278.0 & 219.2 & 154.7 & 115.9 & 0.95 & 1.27 & 1.21 & 1.71 & 2.28 & 0.88 & 2.02\\
      Continuity & 60.9 & 60.9 & 61.2 & 50.8 & 36.8 & 27.2 & 0.99 & 1.21 & 1.20 & 1.66 & 2.24 & 1.00 & 2.24\\
      TKE & 70.1 & 93.2 & 94.3 & 70.1 & 52.2 & 41.9 & 0.99 & 1.34 & 1.33 & 1.78 & 2.23 & 0.75 & 1.67\\
      Mix. Frac. & 68.8 & 91.7 & 86.6 & 62.5 & 45.9 & 36.1 & 1.06 & 1.38 & 1.47 & 2.00 & 2.54 & 0.75 & 1.91\\ [1em]
      \multicolumn{10}{l}{\textbf{Fine $P=1$ mesh (140M HEX-8 elements)}} \\
      \hline
      Momentum & 246.9 & 277.8 & 290.1 & 228.8 & 161.1 & 118.2 & 0.96 & 1.27 & 1.21 & 1.72 & 2.35 & 0.89 & 2.09\\
      Continuity & 64.4 & 64.4 & 65.1 & 54.4 & 38.5 & 28.9 & 0.99 & 1.20 & 1.18 & 1.67 & 2.23 & 1.00 & 2.23\\
      TKE & 73.9 & 97.7 & 99.2 & 73.9 & 55.6 & 44.9 & 0.98 & 1.34 & 1.32 & 1.76 & 2.17 & 0.76 & 1.64\\
      Mix. Frac. & 72.5 & 96.1 & 90.9 & 66.1 & 48.2 & 38.3 & 1.06 & 1.38 & 1.45 & 1.99 & 2.51 & 0.76 & 1.89\\ [1em]
      \multicolumn{10}{l}{\textbf{Coarse $P=2$ mesh (17.5M HEX-27 elements)}} \\
      \hline
      Momentum & -- & 967.3 & 937.6 & 697.7 & 470.3 & 392.2 & 1.03 & 1.34 & 1.39 & 2.06 & 2.47 & -- & --\\
      Continuity & -- & 249.4 & 201.1 & 172.0 & 118.9 & 95.5 & 1.24 & 1.17 & 1.45 & 2.10 & 2.61 & -- & --\\
      TKE & -- & 254.5 & 277.1 & 257.9 & 157.6 & 132.7 & 0.92 & 1.07 & 0.99 & 1.61 & 1.92 & -- & --\\
      Mix. Frac. & -- & 251.7 & 261.4 & 243.0 & 147.4 & 123.6 & 0.96 & 1.08 & 1.04 & 1.71 & 2.04 & -- & --\\
      \hline\hline
    \end{tabular}
  \end{table}
\end{landscape}

\begin{landscape}
  \begin{table}[tb]
    \centering
    \caption{Matrix assembly timing comparisons on KNL partition of NERSC Cori
      system. Code configurations: H -- Hybrid element/node algorithm; B --
      Baseline non-consolidated algorithm; C1 -- consolidated kernel algorithms; C2 --
      C1 with SIMD datatypes; C3 -- C2 with OpenMP threading; C4 -- C3 with
      \code{sumInto(...)} and SIMD interleave optimizations.}
    \label{tab:knl_assembly_timings}
    \begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r}
      \hline\hline
      & \multicolumn{6}{c|}{Matrix assembly time (s)} & \multicolumn{7}{c}{Speedup ratio} \\[0.5em]
      Equation & Hybrid & Baseline & Conf. C1 & Conf. C2 & Conf. C3 & Conf. C4 & B:C1 & C1:C2 & B:C2 & B:C3 & B:C4  & H:B & H:C4\\ [1em]
      \multicolumn{10}{l}{\textbf{Coarse $P=1$ mesh (17.5M HEX-8 elements)}} \\
      \hline
      Momentum & 329.6 & 398.0 & 473.0 & 352.0 & 250.7 & 203.1 & 0.84 & 1.34 & 1.13 & 1.59 & 1.96 & 0.83 & 1.62\\
      Continuity & 91.7 & 91.7 & 98.1 & 73.3 & 54.2 & 41.1 & 0.94 & 1.34 & 1.25 & 1.69 & 2.23 & 1.00 & 2.23\\
      TKE & 117.6 & 156.5 & 170.7 & 101.5 & 81.4 & 64.6 & 0.92 & 1.68 & 1.54 & 1.92 & 2.42 & 0.75 & 1.82\\
      Mix. Frac. & 115.2 & 154.0 & 152.2 & 87.3 & 67.0 & 53.0 & 1.01 & 1.74 & 1.76 & 2.30 & 2.90 & 0.75 & 2.17\\ [1em]
      \multicolumn{10}{l}{\textbf{Fine $P=1$ mesh (140M HEX-8 elements)}} \\
      \hline
      Momentum & 343.0 & 419.4 & 493.0 & 374.9 & 266.2 & 220.9 & 0.85 & 1.32 & 1.12 & 1.58 & 1.90 & 0.82 & 1.55\\
      Continuity & 97.1 & 97.1 & 105.4 & 80.2 & 61.0 & 46.9 & 0.92 & 1.31 & 1.21 & 1.59 & 2.07 & 1.00 & 2.07\\
      TKE & 123.8 & 165.7 & 184.6 & 114.9 & 94.3 & 76.8 & 0.90 & 1.61 & 1.44 & 1.76 & 2.16 & 0.75 & 1.61\\
      Mix. Frac. & 121.6 & 163.3 & 162.6 & 96.7 & 76.4 & 61.5 & 1.00 & 1.68 & 1.69 & 2.14 & 2.66 & 0.74 & 1.98\\ [1em]
      \multicolumn{10}{l}{\textbf{Coarse $P=2$ mesh (17.5M HEX-27 elements)}} \\
      \hline
      Momentum & -- & 1746.8 & 1642.3 & 894.0 & 456.2 & 379.4 & 1.06 & 1.84 & 1.95 & 3.83 & 4.60 & -- & --\\
      Continuity & -- & 370.8 & 308.5 & 228.9 & 114.6 & 94.8 & 1.20 & 1.35 & 1.62 & 3.23 & 3.91 & -- & --\\
      TKE & -- & 449.6 & 496.8 & 290.1 & 146.9 & 126.1 & 0.90 & 1.71 & 1.55 & 3.06 & 3.57 & -- & --\\
      Mix. Frac. & -- & 446.0 & 461.0 & 276.9 & 140.2 & 119.7 & 0.97 & 1.67 & 1.61 & 3.18 & 3.73 & -- & --\\ [1em]
      \hline\hline
    \end{tabular}
  \end{table}
\end{landscape}

\begin{enumerate}
\item The consolidated algorithm design without any NGP enhancements (e.g., SIMD
  and/or OpenMP threading) tend to be slower than both the hybrid and baseline 
  non-consolidated assembly for the low-order simulations on Cori. The disparity
  in performance between consolidated and hybrid simulations can be attributed 
  to the use of only element-based algorithms in the consolidated design as compared 
  to nodal source and time contributions terms employed in the baseline simulations.
  Although the nodal approach involves a separate matrix assemble (along with a separate 
  gather), it avoids a dual nodal volume calculation. However, for the simulation comparison 
  between baseline and consolidated algorithm, the same connectivity graph is used. In fact,
  the baseline includes extra field data gathers for coordinates and the independent
  variables. This must be further explored in future milestone efforts. The Haswell
  performance disparity seems more in line with what the team has seen on local 
  institutional resources while the KNL data seems noteworthy.
\item In contrast to low-order meshes, the high-order $P=2$ mesh matrix assembly
  performance timings are on par with the non-consolidated approach. Here the
  cost of element data gather is amoritized by the extra work performed by
  computational kernels on each element.
\item The introduction of SIMD vectorization recovers the loss in performance
  from consolidated design on both machines for all equations except the
  momentum equation on low-order meshes. However, on high-order mesh the
  momentum equation assembly times show almost a 2x speedup on KNL. This can be
  attributed to the wide vector width ($=8$) available on KNL cores. At this
  point, it appears that the cost of interleaving and de-interleaving data for
  multiple elements is sufficiently amoritized by processing 8 elements per
  instruction, as compared to only 4 on Haswell.
\item Activating OpenMP threading\footnote{The current study used two
    OpenMP threads per MPI rank.} in conjunction with SIMD vectorization further
  increases the gains observed on both machines, especially for the high-order
  $P=2$ mesh where a factor of 3x speedup is observed on KNL machines.
\end{enumerate}


While the performance gains on low-order meshes have been quite modest, the
situation is quite different for the higher-order mesh case, not just in terms
of speedup factors but also the viability of a higher-order pathway in the
ExaWind project. With the baseline non-consolidated approach, the higher order
approach suffered approximately a $4-5\times$ runtime penalty on matrix assembly
when compared to the fine low-order mesh. In contrast, the introduction of SIMD
and OpenMP threading reduce this time difference to a factor of $2$ on KNL.
Furthermore, the runtimes on KNL are slightly faster with the NGP code
compared to Haswell. Of course, further performance studies are necessary to
understand the tradeoffs associated with $P > 2$, and the point of diminishing
returns with respect to the number of threads per MPI rank. However, the
higher-order pathway on next-generation platforms certainly appears encouraging.

\subsection{Code Timing Comparison Between Master and pre-ExaWind Version 1.1}
In this brief section, a high level view of overall application code improvements made to 
Nalu since the beginning of the ExaWind effort is provided. The performance test case is a 
150 million element Vestas V27 (225 kw) wind turbine using a hybrid mesh (hexahedral, tetrahedral, wedge,
and pyramid mesh topologies). The case is run on the Sandia institutional cluster, Sky Bridge (Cray-based
2.6 GHz Sandy Bridge with infiniband interconnect). As has been described, the full master element topology transition
is required for proper Kokkos-based kernel performance testing. As such, this benchmark between
the master code base (09/2017) and version 1.1 (10/2016) is performed using the previously deployed
algorithm implementation in Nalu. Therefore, the timings capture various improvements made to
the Nalu::TpetraLinearSystem class over the year. Highlights of code changes agnostic to the new kernel
design include transitioning to direct Kokkos calls in linear system assembly code and a new \code{sumInto()} 
implementation.

The V27 simulation timings, for purposes of this milestone, are restricted to matrix assembly only. However, 
in general, overall simulation improvements are clear for this case involving parallel searches and the 
DG/CVFEM non-conformal interface. In general, matrix assembly performance is now nearly 1.8 times faster 
for momentum and scalar assembly. The recent re-write of the \code{sumInto()} method alone attributed a 1.2 
times speed-up. This data suggests that as we improve the 
underlying kernel design and Tpetra linear system interfaces, the application code base is continually 
improving in peformance. Linear solver performance regressed a modest 3-5\% over the same development time 
frame. Investigation into this slight regression is ongoing.

\begin{comment}
% BEGIN RECEIVE ORGTBL haswelltimings
\begin{tabular}{lrrrrrrrrrrrrr}
r3 &  &  &  &  &  &  &  &  &  &  &  &  & \\
Momentum & 233.9 & 264.5 & 278.0 & 219.2 & 154.7 & 115.9 & 0.95 & 1.27 & 1.21 & 1.71 & 2.28 & 0.88 & 2.02\\
Continuity & 60.9 & 60.9 & 61.2 & 50.8 & 36.8 & 27.2 & 0.99 & 1.21 & 1.20 & 1.66 & 2.24 & 1.00 & 2.24\\
TKE & 70.1 & 93.2 & 94.3 & 70.1 & 52.2 & 41.9 & 0.99 & 1.34 & 1.33 & 1.78 & 2.23 & 0.75 & 1.67\\
Mix. Frac. & 68.8 & 91.7 & 86.6 & 62.5 & 45.9 & 36.1 & 1.06 & 1.38 & 1.47 & 2.00 & 2.54 & 0.75 & 1.91\\
 &  &  &  &  &  &  &  &  &  &  &  &  & \\
r4 &  &  &  &  &  &  &  &  &  &  &  &  & \\
Momentum & 246.9 & 277.8 & 290.1 & 228.8 & 161.1 & 118.2 & 0.96 & 1.27 & 1.21 & 1.72 & 2.35 & 0.89 & 2.09\\
Continuity & 64.4 & 64.4 & 65.1 & 54.4 & 38.5 & 28.9 & 0.99 & 1.20 & 1.18 & 1.67 & 2.23 & 1.00 & 2.23\\
TKE & 73.9 & 97.7 & 99.2 & 73.9 & 55.6 & 44.9 & 0.98 & 1.34 & 1.32 & 1.76 & 2.17 & 0.76 & 1.64\\
Mix. Frac. & 72.5 & 96.1 & 90.9 & 66.1 & 48.2 & 38.3 & 1.06 & 1.38 & 1.45 & 1.99 & 2.51 & 0.76 & 1.89\\
 &  &  &  &  &  &  &  &  &  &  &  &  & \\
r3\(_{\text{p2}}\) &  &  &  &  &  &  &  &  &  &  &  &  & \\
Momentum & -- & 967.3 & 937.6 & 697.7 & 470.3 & 392.2 & 1.03 & 1.34 & 1.39 & 2.06 & 2.47 & -- & --\\
Continuity & -- & 249.4 & 201.1 & 172.0 & 118.9 & 95.5 & 1.24 & 1.17 & 1.45 & 2.10 & 2.61 & -- & --\\
TKE & -- & 254.5 & 277.1 & 257.9 & 157.6 & 132.7 & 0.92 & 1.07 & 0.99 & 1.61 & 1.92 & -- & --\\
Mix. Frac. & -- & 251.7 & 261.4 & 243.0 & 147.4 & 123.6 & 0.96 & 1.08 & 1.04 & 1.71 & 2.04 & -- & --\\
\end{tabular}
% END RECEIVE ORGTBL haswelltimings

#+ORGTBL: SEND haswelltimings orgtbl-to-latex
| r3         |       |       |       |       |       |       |      |      |      |      |      |      |      |
| Momentum   | 233.9 | 264.5 | 278.0 | 219.2 | 154.7 | 115.9 | 0.95 | 1.27 | 1.21 | 1.71 | 2.28 | 0.88 | 2.02 |
| Continuity |  60.9 |  60.9 |  61.2 |  50.8 |  36.8 |  27.2 | 0.99 | 1.21 | 1.20 | 1.66 | 2.24 | 1.00 | 2.24 |
| TKE        |  70.1 |  93.2 |  94.3 |  70.1 |  52.2 |  41.9 | 0.99 | 1.34 | 1.33 | 1.78 | 2.23 | 0.75 | 1.67 |
| Mix. Frac. |  68.8 |  91.7 |  86.6 |  62.5 |  45.9 |  36.1 | 1.06 | 1.38 | 1.47 | 2.00 | 2.54 | 0.75 | 1.91 |
|            |       |       |       |       |       |       |      |      |      |      |      |      |      |
| r4         |       |       |       |       |       |       |      |      |      |      |      |      |      |
| Momentum   | 246.9 | 277.8 | 290.1 | 228.8 | 161.1 | 118.2 | 0.96 | 1.27 | 1.21 | 1.72 | 2.35 | 0.89 | 2.09 |
| Continuity |  64.4 |  64.4 |  65.1 |  54.4 |  38.5 |  28.9 | 0.99 | 1.20 | 1.18 | 1.67 | 2.23 | 1.00 | 2.23 |
| TKE        |  73.9 |  97.7 |  99.2 |  73.9 |  55.6 |  44.9 | 0.98 | 1.34 | 1.32 | 1.76 | 2.17 | 0.76 | 1.64 |
| Mix. Frac. |  72.5 |  96.1 |  90.9 |  66.1 |  48.2 |  38.3 | 1.06 | 1.38 | 1.45 | 1.99 | 2.51 | 0.76 | 1.89 |
|            |       |       |       |       |       |       |      |      |      |      |      |      |      |
| r3_p2      |       |       |       |       |       |       |      |      |      |      |      |      |      |
| Momentum   |    -- | 967.3 | 937.6 | 697.7 | 470.3 | 392.2 | 1.03 | 1.34 | 1.39 | 2.06 | 2.47 |   -- |   -- |
| Continuity |    -- | 249.4 | 201.1 | 172.0 | 118.9 |  95.5 | 1.24 | 1.17 | 1.45 | 2.10 | 2.61 |   -- |   -- |
| TKE        |    -- | 254.5 | 277.1 | 257.9 | 157.6 | 132.7 | 0.92 | 1.07 | 0.99 | 1.61 | 1.92 |   -- |   -- |
| Mix. Frac. |    -- | 251.7 | 261.4 | 243.0 | 147.4 | 123.6 | 0.96 | 1.08 | 1.04 | 1.71 | 2.04 |   -- |   -- |
\end{comment}

\begin{comment}
% BEGIN RECEIVE ORGTBL knltimings
\begin{tabular}{lrrrrrrrrrrrrr}
r3 &  &  &  &  &  &  &  &  &  &  &  &  & \\
Momentum & 329.6 & 398.0 & 473.0 & 352.0 & 250.7 & 203.1 & 0.84 & 1.34 & 1.13 & 1.59 & 1.96 & 0.83 & 1.62\\
Continuity & 91.7 & 91.7 & 98.1 & 73.3 & 54.2 & 41.1 & 0.94 & 1.34 & 1.25 & 1.69 & 2.23 & 1.00 & 2.23\\
TKE & 117.6 & 156.5 & 170.7 & 101.5 & 81.4 & 64.6 & 0.92 & 1.68 & 1.54 & 1.92 & 2.42 & 0.75 & 1.82\\
Mix. Frac. & 115.2 & 154.0 & 152.2 & 87.3 & 67.0 & 53.0 & 1.01 & 1.74 & 1.76 & 2.30 & 2.90 & 0.75 & 2.17\\
 &  &  &  &  &  &  &  &  &  &  &  &  & \\
r4 &  &  &  &  &  &  &  &  &  &  &  &  & \\
Momentum & 343.0 & 419.4 & 493.0 & 374.9 & 266.2 & 220.9 & 0.85 & 1.32 & 1.12 & 1.58 & 1.90 & 0.82 & 1.55\\
Continuity & 97.1 & 97.1 & 105.4 & 80.2 & 61.0 & 46.9 & 0.92 & 1.31 & 1.21 & 1.59 & 2.07 & 1.00 & 2.07\\
TKE & 123.8 & 165.7 & 184.6 & 114.9 & 94.3 & 76.8 & 0.90 & 1.61 & 1.44 & 1.76 & 2.16 & 0.75 & 1.61\\
Mix. Frac. & 121.6 & 163.3 & 162.6 & 96.7 & 76.4 & 61.5 & 1.00 & 1.68 & 1.69 & 2.14 & 2.66 & 0.74 & 1.98\\
 &  &  &  &  &  &  &  &  &  &  &  &  & \\
r3\(_{\text{p2}}\) &  &  &  &  &  &  &  &  &  &  &  &  & \\
Momentum & -- & 1746.8 & 1642.3 & 894.0 & 456.2 & 379.4 & 1.06 & 1.84 & 1.95 & 3.83 & 4.60 & -- & --\\
Continuity & -- & 370.8 & 308.5 & 228.9 & 114.6 & 94.8 & 1.20 & 1.35 & 1.62 & 3.23 & 3.91 & -- & --\\
TKE & -- & 449.6 & 496.8 & 290.1 & 146.9 & 126.1 & 0.90 & 1.71 & 1.55 & 3.06 & 3.57 & -- & --\\
Mix. Frac. & -- & 446.0 & 461.0 & 276.9 & 140.2 & 119.7 & 0.97 & 1.67 & 1.61 & 3.18 & 3.73 & -- & --\\
\end{tabular}
% END RECEIVE ORGTBL knltimings

#+ORGTBL: SEND knltimings orgtbl-to-latex
| r3         |       |        |        |       |       |       |      |      |      |      |      |      |      |
| Momentum   | 329.6 |  398.0 |  473.0 | 352.0 | 250.7 | 203.1 | 0.84 | 1.34 | 1.13 | 1.59 | 1.96 | 0.83 | 1.62 |
| Continuity |  91.7 |   91.7 |   98.1 |  73.3 |  54.2 |  41.1 | 0.94 | 1.34 | 1.25 | 1.69 | 2.23 | 1.00 | 2.23 |
| TKE        | 117.6 |  156.5 |  170.7 | 101.5 |  81.4 |  64.6 | 0.92 | 1.68 | 1.54 | 1.92 | 2.42 | 0.75 | 1.82 |
| Mix. Frac. | 115.2 |  154.0 |  152.2 |  87.3 |  67.0 |  53.0 | 1.01 | 1.74 | 1.76 | 2.30 | 2.90 | 0.75 | 2.17 |
|            |       |        |        |       |       |       |      |      |      |      |      |      |      |
| r4         |       |        |        |       |       |       |      |      |      |      |      |      |      |
| Momentum   | 343.0 |  419.4 |  493.0 | 374.9 | 266.2 | 220.9 | 0.85 | 1.32 | 1.12 | 1.58 | 1.90 | 0.82 | 1.55 |
| Continuity |  97.1 |   97.1 |  105.4 |  80.2 |  61.0 |  46.9 | 0.92 | 1.31 | 1.21 | 1.59 | 2.07 | 1.00 | 2.07 |
| TKE        | 123.8 |  165.7 |  184.6 | 114.9 |  94.3 |  76.8 | 0.90 | 1.61 | 1.44 | 1.76 | 2.16 | 0.75 | 1.61 |
| Mix. Frac. | 121.6 |  163.3 |  162.6 |  96.7 |  76.4 |  61.5 | 1.00 | 1.68 | 1.69 | 2.14 | 2.66 | 0.74 | 1.98 |
|            |       |        |        |       |       |       |      |      |      |      |      |      |      |
| r3_p2      |       |        |        |       |       |       |      |      |      |      |      |      |      |
| Momentum   |    -- | 1746.8 | 1642.3 | 894.0 | 456.2 | 379.4 | 1.06 | 1.84 | 1.95 | 3.83 | 4.60 |   -- |   -- |
| Continuity |    -- |  370.8 |  308.5 | 228.9 | 114.6 |  94.8 | 1.20 | 1.35 | 1.62 | 3.23 | 3.91 |   -- |   -- |
| TKE        |    -- |  449.6 |  496.8 | 290.1 | 146.9 | 126.1 | 0.90 | 1.71 | 1.55 | 3.06 | 3.57 |   -- |   -- |
| Mix. Frac. |    -- |  446.0 |  461.0 | 276.9 | 140.2 | 119.7 | 0.97 | 1.67 | 1.61 | 3.18 | 3.73 |   -- |   -- |
\end{comment}

\begin{comment}
% BEGIN RECEIVE ORGTBL rundetails
\begin{tabular}{l||r|r|r|r||r|r|r|r}
Code & \multicolumn{4}{c}{Haswell} & \multicolumn{4}{c}{KNL} \\
Configuration & Nodes & MPI ranks & Ranks/node & OMP Threads & Nodes & MPI ranks & Ranks/node & OMP Threads\\
Hybrid & 5 & 160 & 32 & 1 & 5 & 320 & 64 & 1\\
Baseline & 5 & 160 & 32 & 1 & 5 & 320 & 64 & 1\\
C1 & 5 & 160 & 32 & 1 & 5 & 320 & 64 & 1\\
C2 & 5 & 160 & 32 & 1 & 5 & 320 & 64 & 1\\
C3 & 10 & 160 & 16 & 2 & 5 & 320 & 64 & 2\\
C4 & 10 & 160 & 16 & 2 & 5 & 320 & 64 & 2\\
 &  &  &  &  &  &  &  & \\
Hybrid & 40 & 1280 & 32 & 1 & 40 & 2560 & 64 & 1\\
Baseline & 40 & 1280 & 32 & 1 & 40 & 2560 & 64 & 1\\
C1 & 40 & 1280 & 32 & 1 & 40 & 2560 & 64 & 1\\
C2 & 40 & 1280 & 32 & 1 & 40 & 2560 & 64 & 1\\
C3 & 80 & 1280 & 16 & 2 & 40 & 2560 & 64 & 2\\
C4 & 80 & 1280 & 16 & 2 & 40 & 2560 & 64 & 2\\
 &  &  &  &  &  &  &  & \\
Baseline & 40 & 1280 & 32 & 1 & 40 & 2560 & 64 & 1\\
C1 & 40 & 1280 & 32 & 1 & 40 & 2560 & 64 & 1\\
C2 & 40 & 1280 & 32 & 1 & 40 & 2560 & 64 & 1\\
C3 & 80 & 1280 & 16 & 2 & 80 & 2560 & 32 & 2\\
C4 & 80 & 1280 & 16 & 2 & 80 & 2560 & 32 & 2\\
\end{tabular}
% END RECEIVE ORGTBL rundetails

#+ORGTBL: SEND rundetails orgtbl-to-latex
| Configuration | Nodes | MPI ranks | Ranks/node | OMP Threads | Nodes | MPI ranks | Ranks/node | OMP Threads |
| Hybrid        |     5 |       160 |         32 |           1 |     5 |       320 |         64 |           1 |
| Baseline      |     5 |       160 |         32 |           1 |     5 |       320 |         64 |           1 |
| C1            |     5 |       160 |         32 |           1 |     5 |       320 |         64 |           1 |
| C2            |     5 |       160 |         32 |           1 |     5 |       320 |         64 |           1 |
| C3            |    10 |       160 |         16 |           2 |     5 |       320 |         64 |           2 |
| C4            |    10 |       160 |         16 |           2 |     5 |       320 |         64 |           2 |
|               |       |           |            |             |       |           |            |             |
| Hybrid        |    40 |      1280 |         32 |           1 |    40 |      2560 |         64 |           1 |
| Baseline      |    40 |      1280 |         32 |           1 |    40 |      2560 |         64 |           1 |
| C1            |    40 |      1280 |         32 |           1 |    40 |      2560 |         64 |           1 |
| C2            |    40 |      1280 |         32 |           1 |    40 |      2560 |         64 |           1 |
| C3            |    80 |      1280 |         16 |           2 |    40 |      2560 |         64 |           2 |
| C4            |    80 |      1280 |         16 |           2 |    40 |      2560 |         64 |           2 |
|               |       |           |            |             |       |           |            |             |
| Baseline      |    40 |      1280 |         32 |           1 |    40 |      2560 |         64 |           1 |
| C1            |    40 |      1280 |         32 |           1 |    40 |      2560 |         64 |           1 |
| C2            |    40 |      1280 |         32 |           1 |    40 |      2560 |         64 |           1 |
| C3            |    80 |      1280 |         16 |           2 |    80 |      2560 |         32 |           2 |
| C4            |    80 |      1280 |         16 |           2 |    80 |      2560 |         32 |           2 |
\end{comment}
